Appendix A: Code and supplementary figures for simulation and policy analyis

### 2018-01-27 appendix/appendixB.Rmd
yaml and tidy

---
output: pdf_document
---

@@

Computes model parameter estimates on each `stockid` in RAM (after normalizing data) using nimble. Then, estimate common stock measurement (Bmsy, MSY, PGY).

@@

```{r plotting}
## This chunk is optional, just tweaks plot appearance / fonts
library(ggthemes)
library(Cairo)
library(extrafont)
library(hrbrthemes)

>>>>

---
title: "Appendix B: Code for analysis comparing to historical data"
author: "Carl Boettiger"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

Computes model parameter estimates for selected stocks in RAM using NIMBLE. estimate $B_{MSY}$

@@

```{r plotting, include = FALSE}
## This chunk is optional, just tweaks plot appearance / fonts
library(ggthemes)
library(Cairo)
library(extrafont)
library(hrbrthemes)

### 2018-01-27 appendix/appendix_harvestfirst.Rmd
yaml and tidy

---
title: "POMDP comparisons across sigma_m, sigma_g"
author: "Carl Boettiger"
date: "`r Sys.Date()`"
output: 
  github_document: default
  pdf_document: default
---

@@

```{r library, message=FALSE}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
library(gridExtra)
```

```{r optional_plotting_config}
library(ggthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)

@@

```{r colors}
#palette <- ptol_pal()(6)
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45") # berkeley colors

colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: high prior",
                      "biomass",
                      "catch"))
```

>>>>

---
title: "Appendix A: Code and supplementary figures for simulation and policy analyis"
author: "Carl Boettiger"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

```{r library, message=FALSE}
## install package first if necessary.
# devtools::install_github("boettiger-lab/sarsop") 
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
library(gridExtra)
```

```{r optional_plotting_config, include=FALSE}
library(ggthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)

@@

```{r colors}
#palette <- ptol_pal()(6)
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45")
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: high prior",
                      "biomass",
                      "catch"))
```
